Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Set

### 2023-09-29 paper.tex
Update title
Update Title page

%%% Document Specifications %%%
\title{Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set}
\author{Dario Thürkauf}

@@

\begin{document}
\begin{titlepage}
\begin{center}
\vspace{1em}
%\large{Master Thesis}\\
\Large Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Address Set \\
\large \vspace{1em}
Dario Thürkauf \\
\vspace{1em}
\normalsize
PhD candidate, Center for Innovative Finance, University of Basel\\
\vspace{1.5em}
Supervised by \\
\large Prof. Dr. Fabian Schär\\
\vspace{1em}
\normalsize
Professor for Distributed Ledger Technologies and Fintech \\
Center for Innovative Finance, University of Basel
\end{center}

>>>>

%%% Document Specifications %%%
\title{Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Set}
\author{Dario Thürkauf}

@@

\begin{document}
\begin{titlepage}
\begin{center}
\vspace{1em}
%\large{Master Thesis}\\
\Large Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Set \\
\large \vspace{1em}
Dario Thürkauf \\
\vspace{1em}
\normalsize
PhD candidate, Center for Innovative Finance, University of Basel\\
\vspace{1em}
Supervised by \\ \vspace{1em}
\large Prof. Dr. Fabian Schär\\
\vspace{1em}
\normalsize
Professor for Distributed Ledger Technologies and Fintech \\
Center for Innovative Finance, University of Basel
\end{center}
